Untitled

### 2021-05-13 Main_Figures/Regression_Tree_Nectar_Pollen.Rmd
regression tree

# Create a decision tree model
tree <- rpart(Interactions~., data=data_1, cp=.007)
# Visualize the decision tree with rpart.plot
rpart.plot(tree, box.palette="GnOr",tweak = 1.20)

>>>>

# Create a decision tree model
tree <- rpart(Interactions~., data=data_1, cp=.004)
# Visualize the decision tree with rpart.plot
rpart.plot(tree, box.palette="GnOr",tweak = 1.20)
